Fluent statistical computing interfaces for biological data analysis

### 2020-08-04 Rmd/00-d-acknowlegements.Rmd
update acknowledgements

I am deeply grateful to my supervisors: Dianne Cook, Matthew Ritchie, and Paul Harrison. Di has been instrumental in helping me grow as a researcher and teacher; she has been patient and always full of interesting insights and enthusiasm for the practice of doing data analysis. I am sorry that I have not named any of my software after Australian animals. Matt is one of the kindest and most generous scientists I know, thank you for allowing me to be a part of your lab and for all of the lab lunches! Paul has been a great advocate for me and my work, thank you for getting down in the trenches and always being available to help when I nag you about technical difficulties I'm having.

@@

I would not have been able to make it through this PhD if not for the support of friends and family. Thank you to the members of FCC, Casey, Clare, Cyrus, Joy and Margs, for always being a delight and making my sides hurt from laughter and fried chicken. Thank you Michael, Rachel, Robbie, Anna, LP, Laura, Saskia, Lan and Josh for making life more fun. A big thanks to my mum, dad and sister for always being supportive of my choices and listening to my complaints. Finally, thank you to my partner Joy for encouraging me to pursue a PhD and always believing in me, even when I don't believe in myself. I am a better person because of you and I am so happy I get to spend my life with you.

>>>>

I am deeply grateful to my supervisors: Dianne Cook, Matthew Ritchie, and Paul Harrison. Di has been instrumental in helping me grow as a researcher and teacher; she has been patient and always full of interesting insights and enthusiasm for the practice of doing data analysis. Thank you Di for your support and guidance throughout this process. I look forward to keep working with you in the future. Matt is one of the kindest and most generous scientists I know, thank you for allowing me to be a part of your lab and for all of the lab lunches! Paul has been a great advocate for me and my work, thank you for getting down in the trenches and always being available to help when I nag you about technical difficulties I'm having.

@@

I would not have been able to make it through this PhD if not for the support of friends and family. Thank you to the members of FCC, Casey, Clare, Cyrus, Joy and Margs, for always being a delight and making my sides hurt from laughter and fried chicken. Thank you Michael, Wai Keen, Rachel, Robbie, Anna, LP, Laura, Saskia, Kathy, Lan and Josh for making life more fun. A big thanks to my mum, dad and sister for always being supportive of my choices and listening to my complaints. Finally, thank you to my partner Joy for encouraging me to pursue a PhD and always believing in me, even when I don't believe in myself. I am a better person because of you and I am so happy I get to spend my life with you.
